Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-01 R0V0.tex
Merge Ian's changes regarding the main result

\mypara As remarked in \cite{Manchester2014a}, one of the main advantages to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system~\eqref{eq:general system} are recalled below.

@@

\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner. In this paper, these limitations are addressed by imposing a separable structure over $W$.

@@

\begin{definition}\label{def:SSCCM}
	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if it can be decomposed into the following sum
	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}\;,
	\end{equation*}
	where, for each index $i\in\mathbb{N}_{[1,N]}$, and for every $(x_i,\delta_{x_i})\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$, the function $V_i(x_i,\delta_{x_i}):=\delta_{x_i}^\top M_i(x_i)\delta_{x_i}$ is a metric on $\mathbb{R}^{n_i}$.
\end{definition}

\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components. The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).

@@

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\mypara	The MI~\eqref{eq:MI:SSCCM} implies that the inequality
	\begin{equation*}
		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
	\end{equation*}
	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds. Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.

@@

\mypara Since $M$ has a block-diagonal structure, it can be split into $N$ separate optimization problems depending on
different decision variables. Moreover, the positive definiteness of $M$ implies also that the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$. Consequently,
	\begin{equation*}
		\gamma_i=\arg\min e(c_i)\Leftrightarrow\gamma=\arg\min\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
	\end{equation*}
	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.

>>>>

\mypara As remarked in \cite{Manchester2014a}, one of the main advantages to look for control contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system~\eqref{eq:general system} are recalled below.

@@

\mypara From the above steps, even if the problem of imposing a particular structure on $K$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner. In this paper, these limitations are addressed by imposing a separable structure over $W$.

@@

Inspired by the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}), we introduce the following class of control contraction metrics:

\begin{definition}\label{def:SSCCM}
	A control contraction metric $V$ for system \eqref{eq:general system} is called \emph{sum-separable} if it can be decomposed like so:	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}\;,
	\end{equation*}
	where, for each index $i\in\mathbb{N}_{[1,N]}$, and for every $(x_i,\delta_{x_i})\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$, the function $V_i(x_i,\delta_{x_i}):=\delta_{x_i}^\top M_i(x_i)\delta_{x_i}$ is a metric on $\mathbb{R}^{n_i}$.
\end{definition}

\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components, each of which depends only on the {\em local} information $x_i, \delta_{x_i}$.

@@

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\mypara	The MI~\eqref{eq:MI:SSCCM} implies that the inequality
	\begin{equation*}
		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
	\end{equation*}
	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds. Thus, $M$ is a sum-separable control contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.

@@

\mypara Since $M$ has a block-diagonal structure, it can be split into $N$ separate optimization problems depending on
different decision variables. Moreover, the positive definiteness of $M$ implies also that the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$. Consequently,
	\begin{equation*}
		\gamma_i=\arg\min e(c_i),\forall i\in\mathbb{N}_{[1,N]}\,\Leftrightarrow\,\gamma=\arg\min\ell(c).
	\end{equation*}
	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
